Inference of Heating Properties from ``Hot'' Non-flaring Plasmas in Active Region Cores II. Nanoflare Trains

### 2016-03-25 hot_non-flaring_plasma_2/hot_non-flaring_plasma_2.tex
removing outdated figures; heavy editing, cutting out some sections

@@

	\par One strategy for constraining the nanoflare model is analysis of modeled and observed emission measure distributions for signatures of impulsive heating in active region cores. As with cool emission, hot emission is also often described by a power-law relation of the form $\mathrm{EM}\propto T^{-b}$. Typically, this power-law fit to the emission measure is done ``hotward'' of the peak, usually in the range $6.6\lesssim\log{T}\lesssim7.2$. However, measured values of these hotward slopes are poorly constrained due to both the magnitude of emission and the lack of available spectroscopic data in this temperature range. \citet{warren_systematic_2012}, using spectral measurements from EIS, provided hotward fits for $\mathrm{EM}$ reconstructions for a large number of active regions. All measured slopes fell in the range $6.1<b<10.3$, with large uncertainties on each hotward fit.

@@

	\par An often overlooked consequence of impulsive heating in the corona is electron-ion non-equilibrium. In a fully-ionized hydrogen plasma like the solar corona, interactions between electrons and ions are governed by binary Coulomb collisions. For $n\sim10^9~\mathrm{cm}^{-3}$ and $T\sim10^7~\mathrm{K}$, parameters typical of nanoflare heating, the collisional timescale, $\tau_{ei}=1/\nu_{ei}$, where $\nu_{ei}$ is the Coulomb collision frequency (see \autoref{eq:col_freq}) can be estimated as $\tau_{ei}\approx800$ s. Thus, any heating that occurs on a timescale less than 800 s, such as a nanoflare with a duration of $\tau_H\le100$ s, will result in electron-ion non-equilibrium. Chromospheric evaporation, the response from the transition region to the strong coronal heat flux, does lead to an increase in $n$ and thus a decrease in $\tau_{ei}$. However, we maintain that during this initial phase of impulsive heating, $\tau_{ei}\gg\tau_H$ still holds, with 800 s being an approximate upper bound on $\tau_{ei}$. 

@@

	\par In our first paper, \citet{barnes_inference_2016} \citepalias[hereafter]{barnes_inference_2016}, we studied the effect of pulse duration, flux limiting, and NEI on hot emission from single nanoflares and nanoflare trains. In this second paper in our series on hot emission in active region cores, we use an efficient two-fluid hydrodynamic model to explore the effect of electron and ion heating on nanoflare-heated loops. In particular, we look at how the hot emission is affected by heating preferentially one species or the other as well as how this hot emission can vary with heating frequency and the power-law index that determines the event energy distribution. Additionally, we consider how NEI may affect hot emission measure slopes in the cases of electron and ion heating as well as the single-fluid case.

@@

	where $\nu_{ei}$ is the electron-ion binary Coulomb collision frequency and $\psi_{TR}$ is a term included to maintain charge and current and neutrality and is defined in the appendix of \citetalias{barnes_inference_2016}. These equations are closed by the equations of state $p_e=k_BnT_e$ and $p_i=k_BnT_i$.

@@

		\caption{Total Parameter space covered. $\Sigma$ indicates the species that is heated, where ``single'' indicates a single-fluid model. $\alpha$ is the power-law index and $\beta$ indicates the scaling in the relationship $Q\propto T_N^{\beta}$, where $\beta=0$ corresponds to the case where $t_N$ and the event energy are independent. Note that $(3~\alpha~\mathrm{values})\times(3~\beta~\mathrm{values})+\mathrm{uniform~heating}=$ 10 different types of heating functions. \hl{Adjust depending on what value of $\beta$ we use in the end.}}

@@

	\par Recent observations have suggested that loops in active region cores are maintained at an equilibrium temperature of $T_{peak}\approx4$ MK \citep{warren_constraints_2011,warren_systematic_2012}. Using our modified two-fluid EBTEL model, we have estimated the corresponding time-averaged volumetric heating rate for a loop of half-length $L=40$ Mm to be  $H_{eq}\sim4.5\times10^{-3}$. In the single-fluid EBTEL model, this value is slightly lower because losses due to electron-ion collisions are ignored. Thus, to maintain an emission measure peaked about $T_{peak}$, for triangular pulses, the individual event heating rates are constrained by 

@@

	where $t_{total}$ is the total simulation time. Note that if $H_i=H_0$ for all $i$, the uniform heating rate $H_0$ is $H_0=2t_{total}H_{eq}/N\tau$. Thus, for $L=40$ Mm, $A=10^{14}$ cm$^2$, the total amount of energy injected into the loop by one heating event for a loop heated by $N=20$ nanoflares in $t_{tot}=80000$ s is $\varepsilon=LAt_{total}H_{eq}/N\approx7.2\times10^{24}$ erg, consistent with the energy budget of the Parker nanoflare model. 

@@

	\par Determining the heating frequency in active region cores will help to place constraints on the source(s) of heat in the corona. We define the heating frequency in terms of the waiting time, $t_N$, between successive heating events. Following \citet{cargill_active_2014}, the range of waiting times is $250\le T_N\le5000$ s in increments of 250 s, for a total of 20 different possible heating frequencies. Additionally, $t_N$ can be written as $T_N=(T-N\tau_H)/N$, where we fix $T=80000$ s. Note that because $T$ and $\tau_H$ are fixed, as $t_N$ increases, $N$ decreases. Correspondingly, $Q_i$, the energy injected per event, increases according to \autoref{eq:heating_rate_constraint} such that the total energy injected per run is constant, regardless of $t_N$.

@@

		\caption{\textbf{Top left}: uniform heating amplitudes for $T_N=1000$ s; \textbf{Top right:} uniform heating amplitudes for $T_N=5000$ s; \textbf{Bottom left:} power-law distributed heating amplitudes for $\alpha=-1.5$, $T_N=2000$ s; \textbf{Bottom right:} power-law distributed amplitudes for $\alpha=-1.5$ where the wait times depend on the event energies and the mean wait time for both values of $\beta$ is $\langle T_N\rangle=2000$ s.\hl{Adjust depending on what $\beta$ we use in the end.}}

@@

	\par According to the nanoflare heating model of \citet{parker_nanoflares_1988}, turbulent loop footpoint motions twist and stress the field, leading to a buildup and subsequent release of energy. Following \citet{cargill_active_2014}, we let $\varepsilon_i\propto t_{N,i}^{\beta}$, where $\varepsilon_i,t_{N,i}$ are the total energy and waiting time following event $i$, respectively, and $\beta=1,2$ such that the event energy scales either linearly or quadratically with the waiting time. The reasoning for such an expression is as follows. Bursty, nanoflare heating is thought to arise from the stressing and subsequent relaxation of the coronal field. If a sufficient amount of time has elapsed since the last energy release event, the field will have had enough time to ``wind up'' such that the subsequent energy release is large. Conversely, if only a small amount of time has elapsed since the last event, the field will have not had time to become as stressed, resulting in a lower energy event. Thus, this scaling provides a way to incorporate a more physically motivated heating function into a hydrodynamic model which cannot self-consistently determine the heat input based on the evolving magnetic field. \autoref{fig:heating_funcs} shows the various heating functions used for several example $t_N$ values.

@@

	\par We compute the peak heating rate per event in two different ways: 1) the heating rate is uniform such that $H_i=H_0$ for all $i$ and 2) $H_i$ is chosen from a power-law distribution with index $\alpha$ where $\alpha=-1.5,-2.0,$ or $-2.5$. For the second case, it should be noted that, when $T_N\approx5000$ s, $N\sim20$ events, meaning a single run does not accurately represent the distribution of index $\alpha$. Thus, a sufficiently large number of runs, $N_{R}$, are computed for each $t_N$ to ensure that the total number of events is $N_{tot}=N\times N_{R}\sim10^4$ such that the distribution is well-represented. \autoref{fig:parameter_space} shows the parameter space we will explore. For each set of parameters and waiting time $t_N$, we compute the resulting emission measure distribution for $N$ events in a period $T$. This procedure is repeated $N_R$ times until $N\times N_R\sim10^4$ is satisfied.

@@

	\par In our 0D model, the emission measure is calculated using the familiar expression $\mathrm{EM}=n^2(2L)$, where $L$ is the loop half-length. We consider a temperature range of $4.0\le\log{T}\le8.5$ with bin sizes of $\Delta\log{T}=0.01$. At each iteration $i$, the coronal temperature range $[T_0,T_a]$ is calculated from $\bar{T}_e$ (see \autoref{appendix}). For each bin that falls within $[T_0,T_a]$, $\bar{n}_i^2(2L)$ is added to that bin, where $\bar{n}_i$ is the spatially-averaged number density at iteration $i$. The emission measure in each bin is then averaged over the entire simulation period. When measured observationally, $\mathrm{EM}(T)$ is a line-of-sight quantity. Assuming an aspect ratio (i.e. ratio of loop length to loop width) of 10, we apply a correction factor 1/10 to all calculated $\mathrm{EM}$ curves. We do not attempt to apply an advanced forward modeling treatment here and instead reserve such an approach for a future paper. However, while effects due to NEI are neglected in our parameter space exploration, in \autoref{subsec:non-eq_ion} we consider the emission measure due to $T_{eff}$, the effective temperature due to NEI, for several test cases in order to diagnose how this might affect our calculated emission measure slopes.

@@

	\par We first briefly consider the calculated cool emission measure slopes. Looking at the top right panels of \autoref{fig:el_em} and \autoref{fig:ion_em}, we note that in the cases of electron and ion heating, the cool emission measure slopes are consistent with both observational and modeling studies of cool emission in active region cores, having values that fall within the range $2\le a\le5$ \citep[and references therein]{bradshaw_diagnosing_2012}. Furthermore, the cool slopes computed using our new modified EBTEL model, with a heating function of the form $Q\propto T_N^{\beta}$, are consistent with those values reported in \citet{cargill_active_2014} and show a dependence on the waiting time $t_N$.  

@@

			\includegraphics[width=\columnwidth]{figures/{teff_electron_profiles}.pdf}
			\label{fig:teff_el_em}}
			\includegraphics[width=\columnwidth]{figures/{teff_ion_profiles}.pdf}
			\label{fig:teff_ion_em}}
			\includegraphics[width=\columnwidth]{figures/{teff_single_profiles}.pdf}
			\label{fig:teff_single_em}}

@@

			\includegraphics[width=\columnwidth]{figures/{teff_electron_em}.pdf}
			\label{fig:teff_el_derivs}}
			\includegraphics[width=\columnwidth]{figures/{teff_ion_em}.pdf}
			\label{fig:teff_ion_derivs}}
			\includegraphics[width=\columnwidth]{figures/{teff_single_em}.pdf}
			\label{fig:teff_single_derivs}}

@@

			\caption{Non-equilibrium ionization $T$ (solid), $T_{eff}$ (dashed) and $n$ (dot-dashed), profiles (\textbf{left column}) and  $\mathrm{EM}$ distributions (\textbf{right column}) for electron heating (\textbf{top row}), ion heating (\textbf{middle row}), and the single-fluid case (\textbf{bottom row}). In all cases, $L=40$ Mm and the loop is subject to a single pulse of energy $Q\approx10^{25}$ erg with a duration of $\tau_H=100$ s. The values printed on the $\mathrm{EM}$ plots are the resulting emission measure slopes for the cool (blue) and hot (red) slopes for the cases of $\mathrm{EM}$ and $\mathrm{EM}_{eff}$.}

@@

	\begin{figure}[t]
		\includegraphics[width=\columnwidth]{figures/ion_ts_compare.pdf}
		\caption{Single triangular heating pulse with duration $\tau_H=100$ s and total energy $Q\approx10^{25}$ erg injected into only the ions in a loop of half-length $L=40$ Mm. \textbf{Top:} Ion temperature, electron temperature, and coronal number density. \textbf{Bottom:} Ion thermal conduction $(\tau_{C,i})$ and Coulomb collision $(\tau_{ei})$ timescales. The dotted black line at 100 s marks the end of the heating pulse.}
		\label{fig:ion_ts}

@@

	\par This scenario is clearly illustrated by \autoref{fig:ion_ts}. In this test case, we have impulsively heated the ions with a triangular pulse lasting 100 s with total energy $10^{25}$ erg. In the top panel, we see that by the time the electrons come into equilibrium with the ions, the ions have cooled well below their peak temperature and the loop has just begun to fill. Additionally, the bottom panel shows that during the period in which the ions are at their hottest temperatures, $\tau_{C,i}\ll\tau_{ei}$, where $\tau_{C,i}$ is the ion thermal conduction timescale. Thus, while they are being heated, the ions are giving up nearly all of their energy to thermal conduction before they reach equilibrium with the electrons.

@@

		\includegraphics[width=\columnwidth]{figures/{electron_ts_compare}.pdf}
		\label{fig:electron_ts}
		\caption{ Comparison between Coulomb collision timescale $\tau_{ei}$ and electron thermal conduction timescale $\tau_{C,e}$ for the single-pulse example shown in the top row of \autoref{fig:teff_test_case}. The vertical dotted line marks the end of the heating period.}
		\includegraphics[width=\columnwidth]{figures/{electron_single_nt_compare}.pdf}
		\label{fig:ss_em}
		\caption{$n-T$ state space diagram for the single-pulse examples in \autoref{fig:teff_test_case}. In the cases of electron and ion heating, only $T_e$ is shown. The corresponding $\mathrm{EM}$ distributions are overlaid in red.}
	\par To address \autoref{itm:deriv} and \autoref{itm:histos}, we note that the hot sides of the electron heating $\mathrm{EM}$ distributions in \autoref{fig:el_em} have two distinct phases at long $t_N$: the $\mathrm{EM}$ drops off steeply (compared to the single-fluid case) just after the peak and then there is a pronounced hot shoulder near $\log{T}\sim7.3$. These features are missing in the single-fluid case (\autoref{fig:single_em}) where the $\mathrm{EM}$ is nearly linear (in $\log{\mathrm{EM}},\log{T}$) hotward of the peak until the sharp cutoff near $\log{T}\sim7.4$. This is emphasized in the single-pulse $\mathrm{EM}$ distributions for electron heating, ion heating, and the single-fluid case in \autoref{fig:ss_em}. 
	\par Recalling $\mathrm{EM}\sim n^2\tau_{cool}$, the steeper drop in the electron heating $\mathrm{EM}$ just after the peak indicates accelerated cooling relative to the single-fluid case. We attribute this additional cooling to the Coulomb coupling between the electron and ion populations. As seen in the top panel of \autoref{fig:electron_ts}, near $t=100$ s where the heating turns off, the Coulomb collision and thermal conduction timescales are comparable, meaning that conductive cooling is being assisted as the hotter electrons give up energy to the cooler ions. This enhanced cooling can be seen in the much steeper, negative slope in $T$ just after the heating ends in the electron heating $\mathrm{EM}$ distribution (solid) in \autoref{fig:ss_em} as compared to the single-fluid $\mathrm{EM}$ distribution (dot-dashed).
	\par Regarding the hot shoulder at very high $T$ in the case of electron heating, we again refer to \autoref{fig:ss_em}. We note that the hot shoulder region is coincident in $T$ with the portion of the state space where the density is greater in the electron heating case than in the single-fluid case. Thus, the hot shoulder is a result of the loop filling faster in the case of electron heating such that more emission is deposited at these high temperatures. This extra hot emission consequently decreases the hot emission measure slope as calculated by our power-law fit even though the slope just hotward of the peak is steep relative to the single-fluid case.
	\par In the case of ion heating, the emission measure never sees much of the high temperature ($>10^7$ K) regime because the ions have cooled significantly by thermal conduction before they reach equilibrium with the electrons (as illustrated by \autoref{fig:ion_ts}). However, looking at \autoref{fig:ss_em}, we note that for the mid-range hot temperatures just hotward of the peak, the emission due to ion heating exceeds that due to electron heating, tracking closely with the single-fluid case until the sharp cutoff just above $10^7$ K. The cooling in this case is determined entirely by thermal conduction and is not enhanced by Coulomb coupling. This is because, in the case of ion heating, for the early heating phases, Coulomb coupling is a source term and then becomes negligible as the electron and ion populations reach equilibrium.

@@

	\par For hotward emission in the case of ion heating, we note that the effective heating timescale for the electrons is approximately $\tau_{ei}$, the coupling timescale. As seen in \autoref{fig:ion_ts}, for $Q\approx10^{25}$ erg, the electron temperature increases relatively slowly (compared to the heating timescale of the ions) and only gets above several MK once the density has increased significantly. Thus, ionization equilibrium can be assumed because the electrons undergo no direct impulsive heating. In the cases of electron heating and the single-fluid case, the electrons undergo direct impulsive heating when the density is relatively low. This is what leads to the lower-temperature cutoff in $EM_{eff}$: at these high temperatures and low densities, the ionization equilibration timescale is significantly longer than the heating timescale and so these very high temperatures are never seen. 

@@

	All of the data analysis shown in this work was carried out using the IPython system for interactive scientific computing in Python as well as the NumPy and Scipy numerical and scientific Python libraries \citep{perez_ipython:_2007,van_der_walt_numpy_2011}. All plots were produced using the Matplotlib graphics environment \citep{hunter_matplotlib:_2007}.

>>>>

	\par Several workers have modeled both steady and impulsive heating in coronal loops. 

@@

	\par An important parameter for any proposed coronal heating mechanism is the frequency of energy release. Nanoflare heating is often classified as either \textit{high-frequency} or \textit{low-frequency} heating. In the case of high-frequency heating, $t_N$, the time between successive events, is such that $t_N\ll\tau_c$, where $\tau_c$ is the loop cooling time, and in the case of low-frequency heating $t_N\gg\tau_c$. Steady heating is just high-frequency heating in the limit $t_N\to0$.

@@

	\par One strategy for constraining the nanoflare model is analysis of modeled and observed emission measure distributions for signatures of impulsive heating in active region (AR) cores. As with cool emission, hot emission is also often described by a power-law relation of the form $\mathrm{EM}\propto T^{-b}$. Typically, this power-law fit to the emission measure is done ``hotward'' of the peak, usually in the range $6.6\lesssim\log{T}\lesssim7.2$. However, measured values of these hotward slopes are poorly constrained due to both the magnitude of emission and the lack of available spectroscopic data in this temperature range. \citet{warren_systematic_2012}, using spectral measurements from EIS, provided hotward fits for $\mathrm{EM}$ reconstructions for a large number of ARs. All measured slopes fell in the range $6.1<b<10.3$, with large uncertainties on each hotward fit.
	\par\hl{Cut, repeat of Paper 1} An often overlooked consequence of impulsive heating in the corona is electron-ion non-equilibrium. In a fully-ionized hydrogen plasma like the solar corona, interactions between electrons and ions are governed by binary Coulomb collisions. For $n\sim10^9~\mathrm{cm}^{-3}$ and $T\sim10^7~\mathrm{K}$, parameters typical of nanoflare heating, the collisional timescale, $\tau_{ei}=1/\nu_{ei}$, where $\nu_{ei}$ is the Coulomb collision frequency (see \autoref{eq:col_freq}) can be estimated as $\tau_{ei}\approx800$ s. Thus, any heating that occurs on a timescale less than 800 s, such as a nanoflare with a duration of $\tau_H\le100$ s, will result in electron-ion non-equilibrium. Chromospheric evaporation, the response from the transition region to the strong coronal heat flux, does lead to an increase in $n$ and thus a decrease in $\tau_{ei}$. However, we maintain that during this initial phase of impulsive heating, $\tau_{ei}\gg\tau_H$ still holds, with 800 s being an approximate upper bound on $\tau_{ei}$. 

@@

	\par In our first paper, \citet{barnes_inference_2016} \citepalias[hereafter]{barnes_inference_2016}, we studied the effect of pulse duration, flux limiting, and NEI on hot emission from single nanoflares. In this second paper in our series on hot emission in AR cores, we use an efficient two-fluid hydrodynamic model to explore the effect of electron and ion heating on nanoflare-heated loops. In particular, we look at how the hot emission is affected by heating preferentially one species or the other as well as how this hot emission can vary with heating frequency and the power-law index that determines the event energy distribution. Additionally, we consider how NEI may affect hot emission measure slopes in the cases of electron and ion heating as well as the single-fluid case.

@@

	where $\nu_{ei}$ is the electron-ion binary Coulomb collision frequency and $\psi_{TR}$ is a term included to maintain charge and current and neutrality. These equations are closed by the equations of state $p_e=k_BnT_e$ and $p_i=k_BnT_i$. A full discrussion and derivation of these 0D two-fluid equations can be found in the appendix of \citetalias{barnes_inference_2016}.

@@

		\caption{Total Parameter space covered. $\Sigma$ indicates the species that is heated, where ``single'' indicates a single-fluid model. $\alpha$ is the power-law index and $\beta$ indicates the scaling in the relationship $Q\propto T_N^{\beta}$, where $\beta=0$ corresponds to the case where $t_N$ and the event energy are independent. Note that $(3~\alpha~\mathrm{values})\times(3~\beta~\mathrm{values})+\mathrm{uniform~heating}=$ 10 different types of heating functions. \hl{Adjust depending on what value of $\beta$ we use in the end.	}}

@@

	\par Recent observations have suggested that loops in AR cores are maintained at an equilibrium temperature of $T_{peak}\approx4$ MK \citep{warren_constraints_2011,warren_systematic_2012}. Using our modified two-fluid EBTEL model, we have estimated the corresponding time-averaged volumetric heating rate for a loop of half-length $L=40$ Mm to be  $H_{eq}\sim4.5\times10^{-3}$. In the single-fluid EBTEL model, this value is slightly lower because losses due to electron-ion collisions are ignored. Thus, to maintain an emission measure peaked about $T_{peak}$, for triangular pulses, the individual event heating rates are constrained by 

@@

	where $t_{total}$ is the total simulation time. Note that if $H_i=H_0$ for all $i$, the uniform heating rate $H_0$ is $H_0=2t_{total}H_{eq}/N\tau$. Thus, for $L=40$ Mm, $A=10^{14}$ cm$^2$, the total amount of energy injected into the loop by one heating event for a loop heated by $N=20$ nanoflares in $t_{tot}=8\times10^4$ s is $\varepsilon=LAt_{total}H_{eq}/N\approx7.2\times10^{24}$ erg, consistent with the energy budget of the Parker nanoflare model. 

@@

	\par Determining the heating frequency in AR cores will help to place constraints on the source(s) of heat in the corona. We define the heating frequency in terms of the waiting time, $t_N$, between successive heating events. Following \citet{cargill_active_2014}, the range of waiting times is $250\le t_N\le5000$ s in increments of 250 s, for a total of 20 different possible heating frequencies. Additionally, $t_N$ can be written as $t_N=(t_{total}-N\tau)/N$, where we fix $T=8\times10^4$ s. Note that because $t_{total}$ and $\tau$ are fixed, as $t_N$ increases, $N$ decreases. Correspondingly, $\varepsilon_i$, the energy injected per event, increases according to \autoref{eq:heating_rate_constraint} such that the total energy injected per run is constant, regardless of $t_N$.

@@

		\caption{\textbf{Top}: uniform heating amplitudes for $t_N=1000$ s; \textbf{Middle:} uniform heating amplitudes for $t_N=5000$ s; \textbf{Bottom:} Heating amplitudes drawn from a power-law distribution with index $\alpha=-1.5$. The events shown in red have wait times that depend on the previous event energy while the events shown in blue have uniform wait times. The mean wait time in both cases is $\langle T_N\rangle=2000$ s.}

@@

		\includegraphics[width=\columnwidth]{figures/heating_event_distributions.pdf}
		\caption{Power-law distributions of heating events for indices $\alpha=-1.5,-2.0,-2.5$ for a given heating frequency, $t_N=2500$ s. For each frequency, $t_N$, we compute $N_R$ runs such that the total number of events simulated for each $t_N$ is $N\times N_R\sim10^4$.}
		\label{fig:event_dist}
	\par According to the nanoflare heating model of \citet{parker_nanoflares_1988}, turbulent loop footpoint motions twist and stress the field, leading to a buildup and subsequent release of energy. Following \citet{cargill_active_2014}, we let $\varepsilon_i\propto t_{N,i}^{\beta}$, where $\varepsilon_i,t_{N,i}$ are the total energy and waiting time following event $i$, respectively, and $\beta=1,2$ such that the event energy scales either linearly or quadratically with the waiting time. The reasoning for such an expression is as follows. Bursty, nanoflare heating is thought to arise from the stressing and subsequent relaxation of the coronal field. If a sufficient amount of energy is released into the loop, the field will need enough time to ``unravel'' and ``wind up'' again before the next event such that the subsequent waiting time is large. Conversely, if only a small amount of energy is released, the field will require a shorter unwinding time, resulting in a shorter interval between the subsequent events. Thus, this scaling provides a way to incorporate a more physically motivated heating function into a hydrodynamic model which cannot self-consistently determine the heat input based on the evolving magnetic field. \autoref{fig:heating_funcs} shows the various heating functions used for several example $t_N$ values.

@@

	\par We compute the peak heating rate per event in two different ways: 1) the heating rate is uniform such that $H_i=H_0$ for all $i$ and 2) $H_i$ is chosen from a power-law distribution with index $\alpha$ where $\alpha=-1.5,-2.0,$ or $-2.5$. For the second case, it should be noted that, when $t_N\approx5000$ s, $N\sim20$ events, meaning a single run does not accurately represent the distribution of index $\alpha$. Thus, a sufficiently large number of runs, $N_{R}$, are computed for each $t_N$ to ensure that the total number of events is $N_{tot}=N\times N_{R}\sim10^4$ such that the distribution is well-represented. \autoref{fig:parameter_space} shows the parameter space we will explore. For each set of parameters and waiting time $t_N$, we compute the resulting emission measure distribution for $N$ events in a period $t_{total}$. This procedure is repeated $N_R$ times until $N\times N_R\sim10^4$ is satisfied.

@@

	\par In our 0D model, the emission measure is calculated using the familiar expression $\mathrm{EM}=n^2(2L)$, where $L$ is the loop half-length. We consider a temperature range of $4.0\le\log{T}\le8.5$ with bin sizes of $\Delta\log{T}=0.01$. At each iteration $i$, the coronal temperature range $[T_0,T_a]$ is calculated from $\bar{T}_e$. For each bin that falls within $[T_0,T_a]$, $\bar{n}_i^2(2L)$ is added to that bin, where $\bar{n}_i$ is the spatially-averaged number density at iteration $i$. The emission measure in each bin is then averaged over the entire simulation period. When measured observationally, $\mathrm{EM}(T)$ is a line-of-sight quantity. Assuming an aspect ratio (i.e. ratio of loop length to loop width) of 10, we apply a correction factor 1/10 to all calculated $\mathrm{EM}$ curves. We do not attempt to apply an advanced forward modeling treatment here and instead reserve such an approach for a future paper. However, while effects due to NEI are neglected in our parameter space exploration, in \autoref{subsec:non-eq_ion} we consider the emission measure due to $T_{eff}$, the effective temperature due to NEI, for several test cases in order to diagnose how this might affect our calculated emission measure slopes.

@@

	\par We first briefly consider the calculated cool emission measure slopes. Looking at the top right panels of \autoref{fig:el_em} and \autoref{fig:ion_em}, we note that in the cases of electron and ion heating, the cool emission measure slopes are consistent with both observational and modeling studies of cool emission in AR cores, having values that fall within the range $2\le a\le5$ \citep[and references therein]{bradshaw_diagnosing_2012}. Furthermore, the cool slopes computed using our new modified EBTEL model, with a heating function of the form $Q\propto T_N^{\beta}$, are consistent with those values reported in \citet{cargill_active_2014} and show a dependence on the waiting time $t_N$.  

@@

@@

@@

			\caption{Figures for the cases of non-equilibrium ionization.}

@@

@@

@@

@@

	\par For hotward emission in the case of ion heating, we note that the effective heating timescale for the electrons is approximately $\tau_{ei}$, the coupling timescale. For $Q\approx10^{25}$ erg, the electron temperature increases relatively slowly (compared to the heating timescale of the ions) and only gets above several MK once the density has increased significantly. Thus, ionization equilibrium can be assumed because the electrons undergo no direct impulsive heating. In the cases of electron heating and the single-fluid case, the electrons undergo direct impulsive heating when the density is relatively low. This is what leads to the lower-temperature cutoff in $EM_{eff}$: at these high temperatures and low densities, the ionization equilibration timescale is significantly longer than the heating timescale and so these very high temperatures are never seen. 

@@

	\hl{Move this to results eventually.} All of the data analysis shown in this work was carried out using the IPython system for interactive scientific computing in Python as well as the NumPy and Scipy numerical and scientific Python libraries \citep{perez_ipython:_2007,van_der_walt_numpy_2011}. All plots were produced using the Matplotlib graphics environment \citep{hunter_matplotlib:_2007}.
